MSOA domestic Electricty and Gas maps

### 2021-08-17 MSOA domestic Elec and Gas.Rmd
added leaflet example for pretty plots

```{r Mapping the change in dom mean gas comsumption}
merged_domgas$MSOA11CD <- merged_domgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
ggplot2::ggplot(msoa_domgas20102019) +
  geom_sf(aes(fill=mc_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
##END

>>>>

```{r Mapping the change in dom mean gas comsumption}
merged_domgas$MSOA11CD <- merged_domgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
ggplot2::ggplot(msoa_domgas20102019) +
  geom_sf(aes(fill=mc_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

Use leaflet version to place geo tile underlay

First check co-ord system so matches leaflet

```{r checkLeaflet}
# https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
library(leaflet)

st_coord_sys <- st_crs(msoa_domgas20102019) # check coord system
st_coord_sys$epsg # current coord system ? Leaflet wants EPSG: 4326

# transform the coord system if required
if(st_coord_sys$epsg != 4326){
  map_df_trans <- st_transform(msoa_domgas20102019, "+proj=longlat +datum=WGS84")
}
```

Plot the leaflet map

```{r mapDiffLeaflet, fig.cap="Change in mean domestic gas kWh/meter"}

#h/t @tom_rushby - see also https://rstudio.github.io/leaflet/colors.html

qpal <- colorNumeric("Reds", map_df_trans$mc_diff, n = 9)

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(mc_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

## END
